Formalization of Forcing in Isabelle/ZF \thanks{Supported by Secyt-UNC project 33620180100465CB and Conicet.}

### 2020-01-25 IJCAR2020/absoluteness.tex
código de síntesis y saco ese apéndice de mierda

Once this class versions of the axioms are set up, it is not hard to
apply our synthesis method to obtain their internal, first-order
counterparts.
\begin{framed}
  Some code for axiom synthesis.
\end{framed}

>>>>

Once this class versions of the axioms are set up, it is not hard to
apply our synthesis method to obtain their internal, first-order
counterparts.\footnote{It should be noted that our method for
  synthetic definition requires that the schematic goal had a
  particular format where the only unbound schematic variable occurs
  as an (open) formula whose satisfaction is equivalent to some
  relativized predicate.}
For the case of the Union Axiom, the statement for classes is the
following
\begin{isabelle}
upair{\isacharunderscore}ax{\isacharparenleft}C{\isacharparenright}{\isacharequal}{\isacharequal}{\isasymforall}x{\isacharbrackleft}C{\isacharbrackright}{\isachardot}{\isasymforall}y{\isacharbrackleft}C{\isacharbrackright}{\isachardot}{\isasymexists}z{\isacharbrackleft}C{\isacharbrackright}{\isachardot}\ upair{\isacharparenleft}C{\isacharcomma}x{\isacharcomma}y{\isacharcomma}z{\isacharparenright}
\end{isabelle}
where \isatt{upair} says that \isatt{z} is the unordered pair of
\isatt{x} and \isatt{y}, relative to \isatt{C}.

The following schematic lemma synthesizes its internal version,
\begin{isabelle}
\isacommand{schematic{\isacharunderscore}goal}\isamarkupfalse%
\ ZF{\isacharunderscore}pairing{\isacharunderscore}auto{\isacharcolon}\isanewline
\ \ \ \ {\isachardoublequoteopen}upair{\isacharunderscore}ax{\isacharparenleft}{\isacharhash}{\isacharhash}A{\isacharparenright}\ {\isasymlongleftrightarrow}\ {\isacharparenleft}A{\isacharcomma}\ {\isacharbrackleft}{\isacharbrackright}\ {\isasymTurnstile}\ {\isacharquery}zfpair{\isacharparenright}{\isachardoublequoteclose}\isanewline
\isacommand{unfolding}\isamarkupfalse%
\ upair{\isacharunderscore}ax{\isacharunderscore}def\ \isanewline
\ \ \isacommand{by}\isamarkupfalse%
\ {\isacharparenleft}{\isacharparenleft}rule\ sep{\isacharunderscore}rules\ {\isacharbar}\ simp{\isacharparenright}{\isacharplus}{\isacharparenright}
\end{isabelle}
(the actual formula obtained is
\isatt{Forall(Forall(Exists(upair{\isacharunderscore}fm(2,1,0))))}) and
our \isatt{synthesize} method introduces a new term
\isatt{ZF{\isacharunderscore}pairing{\isacharunderscore}fm} for it.
\begin{isabelle}
\isacommand{synthesize}\isamarkupfalse%
\ {\isachardoublequoteopen}ZF{\isacharunderscore}pairing{\isacharunderscore}fm{\isachardoublequoteclose}\ \isakeyword{from{\isacharunderscore}schematic}\ {\isachardoublequoteopen}ZF{\isacharunderscore}pairing{\isacharunderscore}auto{\isachardoublequoteclose}%
\end{isabelle}
